Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2021-01-09 submission/NatCom_nlp_models.tex
full pass to revise cv discussion, revise comments, revise response
figure 8 updated
GPT2 images ren amed and fixed
XXX filled in

\begin{figure}[hbt!] %[t]
    \centering
    \subfigure[Log Spectral Norm ($\log\Vert\mathbf{W}\Vert_{\infty}$)]{
        \includegraphics[width=5.5cm]{img/GPT-snorm-hist.png}
        \label{fig:GPT-snorm-hist}
       }
    \qquad
    \subfigure[PL exponent ($\alpha$)]{
        \includegraphics[width=5.5cm]{img/GPT-alpha-hist.png}
        \label{fig:GPT-alpha-hist}
       }
   \caption{Histogram of PL exponents 
           %($\alpha$) 
           and Log Spectral Norms 
           %($\log\Vert\mathbf{W}\Vert_{\infty}$) 
           for weight matrices from the OpenAI GPT and GPT2-small pretrained models.}

@@

From Figure~\ref{fig:gpt2-alpha-hist}, we see that
$\bar{\alpha}$, the average $\alpha$ value, decreases with increasing model size (XXX for GPT2-medium, XXX for GPT2-large, and XXX for GPT2-xl), although the differences are less noticeable between the differing well-trained versus very-well-trained GTP2 models than between the poorly-trained versus well-trained GPT and GPT2-small models.
Also, from Figure~\ref{fig:gpt2-pnorm-hist}, we see that, 
unlike GPT, the layer Log Alpha Norms behave more as expected for GPT2 layers, with the larger models consistently having smaller norms (XXX for GPT2-medium, XXX for GPT2-large, and XXX for GPT2-xl). 
Similarly, the Log Spectral Norm also decreases on average with the larger models (XXX for GPT2-medium, XXX for GPT2-large, and XXX for GPT2-xl).
% (not shown).  
As expected, the norm metrics can indeed distinguish among well-trained versus very-well-trained models.

@@

\begin{figure}[htb]
    \centering

    \subfigure[PL exponent ($\alpha$)]{
        \includegraphics[width=5.5cm]{img/GPT2*_fnl_alpha_hist.png}
        \label{fig:gpt2-alpha-hist}
    }
    \quad
    \subfigure[Log Alpha Norm]{
        \includegraphics[width=5.5cm]{img/GPT2*_fnl_logpnorm_hist.png}
        \label{fig:gpt2-pnorm-hist}
    }
    \caption{Histogram of PL exponents 
             %($\alpha$)
             and Log Alpha Norm 
             %($\log\Vert\mathbf{X}\Vert_{\alpha}^{\alpha}$) 
             for weight matrices from models of different sizes in the GPT2 architecture series.  (Plots omit the first 2 (embedding) layers, because they are normalized differently giving anomalously large values.)
             }
    \label{fig:gpt2-histograms}
\end{figure}

>>>>

\begin{figure}[hbt!] %[t]
    \centering
    \subfigure[Log Spectral Norm ($\log\Vert\mathbf{W}\Vert_{\infty}$)]{
        \includegraphics[width=5.5cm]{img/GPT-snorm-hist.png}

        \label{fig:GPT-snorm-hist}
       }
    \qquad
    \subfigure[PL exponent ($\alpha$)]{
      \includegraphics[width=5.5cm]{img/GPT-alpha-hist.png}
      \label{fig:GPT-alpha-hist}
       }
   \caption{Histogram of PL exponents 
           %($\alpha$) 
           and Log Spectral Norms 
           %($\log\Vert\mathbf{W}\Vert_{\infty}$) 
           for weight matrices from the OpenAI GPT and GPT2-small pretrained models.}

@@

From Figure~\ref{fig:gpt2-alpha-hist}, we see that
$\bar{\alpha}$, the average $\alpha$ value, decreases with increasing model size ($3.82$ for GPT2-medium, $3.97$ for GPT2-large, and $3.81$ for GPT2-xl), although the differences are less noticeable between the differing well-trained versus very-well-trained GTP2 models than between the poorly-trained versus well-trained GPT and GPT2-small models.
Also, from Figure~\ref{fig:gpt2-pnorm-hist}, we see that, 
unlike GPT, the layer Log Alpha Norms behave more as expected for GPT2 layers, with the larger models consistently having smaller norms ($9.96$ for GPT2-medium, $7.982$ for GPT2-large, and $7.49$ for GPT2-xl). 
Similarly, the Log Spectral Norm also decreases on average with the larger models ($2.58$ for GPT2-medium, $1.99$ for GPT2-large, and $1.92$ for GPT2-xl).
As expected, the norm metrics can indeed distinguish among well-trained versus very-well-trained models.

@@

\begin{figure}[htb]
    \centering
    \subfigure[PL exponent ($\alpha$)]{
        \includegraphics[width=5.5cm]{img/GPT2_fnl_alpha_hist.png}
        \label{fig:gpt2-alpha-hist}
    }
    \quad
    \subfigure[Log Alpha Norm]{
        \includegraphics[width=5.5cm]{img/GPT2_fnl_log_alpha_norm_hist.png}
        \label{fig:gpt2-pnorm-hist}
    }
    \caption{Histogram of PL exponents 
             %($\alpha$)
             and Log Alpha Norm 
             %($\log\Vert\mathbf{X}\Vert_{\alpha}^{\alpha}$) 
             for weight matrices from models of different sizes in the GPT2 architecture series.  (Plots omit the first 2 (embedding) layers, because they are normalized differently giving anomalously large values.)
             }
    \label{fig:gpt2-histograms}
\end{figure}
